The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-16 paper.tex
update

  Although the high-energy CRe ($10$ -- $100$ GeV) plays a crucial role in reproducing the $\gamma$-ray map\
  within the range of $1$ -- $100$ GeV, we assume the pressure of CRe is much less than that of gas\
  throughout the simulation so that we , and the \textit{Fermi} bubbles can be outlined against the eROSITA bubbles.

@@

 The most interesting finding is that there is a innermost bubbles\
 (dashed box in left top panel of \Cref{fig__jetI5+ismSeed3-45deg})\
 extending out from the Galactic center on either side of the thin disk.\
 The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$ -- $10^{-2}$ cm$^{-3}$),\
 and underpressured with respect to the turbulent plasma.\
 Moreover, the close-up view of profiles around $z=3.7$ kpc (right column in \Cref{fig__profile})
 demonstrates that there is a sharp pressure jump and dense shell at $z=3.61$ kpc,\
 indicating that the innermost bubbles are an expanding reverse shock.\
 We also find that the turbulent plasma is bracketed between the downstream of reverse shock\
 and of the outermost forward shock, thus heating the turbulent plasma up considerably.

@@

  \Cref{fig__xray_0.8keV_angle_000} shows\
  the comparison between simulated (top) and observed (bottom) all-sky map\
  in the range 0.6 -- 1.0 keV at 12.39 Myr and the present time, respectively.\
  In the simulated map, the red arrow at the center of map represents the direction of the bipolar jet,\
  constantly ejecting at an angle of $45^{\circ}$ to the disc normal between 0 -- 1.2 Myr.

@@

% 2. North Polar Spur is not shown as it is a supernova remanent near us.
  Third, the innermost bubbles\
  shown in \Cref{fig__jetI5+ismSeed3-45deg},\
  even though with high column density, is invisible in the simulated X-ray map as\
  the temperature of innermost bubbles is around $1$ -- $10$ eV\
  (see the temperature profile in \Cref{fig__profile}).\
  Consequently, the X-ray emission within the innermost bubbles
  is severely suppressed by the cutoff $\exp\left[-h\nu/k_{B}T\right]$ in the thermal Bremsstrahlung emissivity.\
  This is the reason why the innermost bubbles is unseen in the observation.

  \begin{figure*}
    \subfigure[Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
               (photons s$^{-1}$ deg$^{-2}$) in the 0.6 -- 1.0 keV range.\
               Throughout this paper we show sky maps\
               in Galactic coordinates centered on the Galactic center using a Hammer-Aitoff projection,\
               and observed from the solar system.\
               The red arrow at the center of the\
               top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
               to the disc normal in 1.2 Myr.]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xraymap.png}
      \label{fig__xray_0.8keV_angle_000}
     }
    \subfigure[Comparison of simulated (red) and observed (black; \citealt{Predehl2020}) one-dimensional\
               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
               cut at various galactic latitudes (as labelled).]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xray-profile-0.8keV-000.png}
      \label{fig__x-ray-profile-0.8keV-000}
     }
    \caption{}
    \label{fig_xray-map}
  \end{figure*}

@@

Third, the gamma-ray spectra for all latitudes indicate a spectral cutoff around energies 400 -- 500 GeV,\
consistent with the observed cutoff energy.\
This is expected since
the upscattered high-energy photons ($\epsilon_{1}\sim450$ GeV) mainly arise from\
the scatterings between the relativistic CRe ($\gtrapprox 408$ GeV)\
and optical starlight ($\epsilon \sim 10$ eV),\
and therefore \Cref{gamma-min} can be reduced to $\epsilon_{1}\sim\gamma m_{\text{e}}c^2$\
in the Klein--Nishina limit\
$\left(\text{i.e. }\epsilon_{1}\epsilon \gg \left(m_{\text{e}}c^2\right)^2\right)$,\
implying most of the CRe energy is carried away by the upscattered photons.

>>>>

  Although the high-energy CRe ($10$--$100$ GeV) plays a crucial role in reproducing the $\gamma$-ray map\
  within the range of $1$--$100$ GeV, we assume the pressure of CRe is much less than that of gas\
  throughout the simulation so that we , and the \textit{Fermi} bubbles can be outlined against the eROSITA bubbles.

@@

 The most interesting finding is that there is a innermost bubbles\
 (dashed box in left top panel of \Cref{fig__jetI5+ismSeed3-45deg})\
 extending out from the Galactic center on either side of the thin disk.\
 The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$--$10^{-2}$ cm$^{-3}$),\
 and underpressured with respect to the turbulent plasma.\
 Moreover, the close-up view of profiles around $z=3.7$ kpc (right column in \Cref{fig__profile})
 demonstrates that there is a sharp pressure jump and dense shell at $z=3.61$ kpc,\
 indicating that the innermost bubbles are an expanding reverse shock.\
 We also find that the turbulent plasma is bracketed between the downstream of reverse shock\
 and of the outermost forward shock, thus heating the turbulent plasma up considerably.

@@

  \Cref{fig__xray_0.8keV_angle_000} shows\
  the comparison between simulated (top) and observed (bottom) all-sky map\
  in the range 0.6--1.0 keV at 12.39 Myr and the present time, respectively.\
  In the simulated map, the red arrow at the center of map represents the direction of the bipolar jet,\
  constantly ejecting at an angle of $45^{\circ}$ to the disc normal between 0--1.2 Myr.

@@

% 2. North Polar Spur is not shown as it is a supernova remanent near us.
  Third, the innermost bubbles\
  shown in \Cref{fig__jetI5+ismSeed3-45deg},\
  even though with high column density, is invisible in the simulated X-ray map as\
  the temperature of innermost bubbles is around $1$--$10$ eV\
  (see the temperature profile in \Cref{fig__profile}).\
  Consequently, the X-ray emission within the innermost bubbles
  is severely suppressed by the cutoff $\exp\left[-h\nu/k_{B}T\right]$ in the thermal Bremsstrahlung emissivity.\
  This is the reason why the innermost bubbles is unseen in the observation.

  \begin{figure*}
    \subfigure[Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
               (photons s$^{-1}$ deg$^{-2}$) in the 0.6--1.0 keV range.\
               Throughout this paper we show sky maps\
               in Galactic coordinates centered on the Galactic center using a Hammer-Aitoff projection,\
               and observed from the solar system.\
               The red arrow at the center of the\
               top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
               to the disc normal in 1.2 Myr.]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xraymap.png}
      \label{fig__xray_0.8keV_angle_000}
     }
    \subfigure[Comparison of simulated (red) and observed (black; \citealt{Predehl2020}) one-dimensional\
               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
               cut at various galactic latitudes (as labelled).]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xray-profile-0.8keV-000.png}
      \label{fig__x-ray-profile-0.8keV-000}
     }
    \caption{}
    \label{fig_xray-map}
  \end{figure*}

@@

Third, the gamma-ray spectra for all latitudes indicate a spectral cutoff around energies 400--500 GeV,\
consistent with the observed cutoff energy.\
This is expected since
the upscattered high-energy photons ($\epsilon_{1}\sim450$ GeV) mainly arise from\
the scatterings between the relativistic CRe ($\gtrapprox 408$ GeV)\
and optical starlight ($\epsilon \sim 10$ eV),\
and therefore \Cref{gamma-min} can be reduced to $\epsilon_{1}\sim\gamma m_{\text{e}}c^2$\
in the Klein--Nishina limit\
$\left(\text{i.e. }\epsilon_{1}\epsilon \gg \left(m_{\text{e}}c^2\right)^2\right)$,\
implying most of the CRe energy is carried away by the upscattered photons.
